### 2013-12-13 article2013.Rmd
Muutin päivämäärän
Koodin korjailua, korrelaatiokokeet ja maaryhmäkappaleen poisto
Korjasin koodia niin että hajontakuviot ovat oikein paperissa.

Katsoin läpi shinylla tehdyn korrelaatiokoneen ja kokosin selkeimmät yhteydet dokkariin correlations.

Otin tekstistä pois maaryhmiä koskevan teorialuvun.

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% December 11, 2013

@@

>From the perspective of value structure, the role of "socialist or soviet legacy" in poverty attributions is worth of considering. Murthi and Tiongson (2008) reviewed large body of literature on East-West differences in preferences for redistribution of which vast majority supported the "socialist legacy". By socialist legacy they meant that "owing to the legacy of the past there is a strong preference for income equality and redistributive state spending in post-socialist countries". While testing the findings of previous studies on East-West differences, this study explores the effect of country groups with different socialist and post-socialist past. In order to explore the differences between market economies and post-socialist countries, but also within the "ex-soviet bloc", the study divides post-socialist countries into two groups: Central Eastern Europe (CEE) and Commonwealth of Independent States (CIS) countries. In order to examine the distinctiveness of post-socialist perceptions descriptive analyses include also a selection of Western European countries.

>>>>

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% December 12, 2013

@@
